Adaptive Preregistration for Modelling

### 2024-03-12 preregistration_modelling.qmd
Add Jian as author to template

---
title: "Adaptive Preregistration for Modelling"
subtitle: "A template suitable for use in Ecology and Conservation with accompanying rationale and explanation."
description: "Note: Black boxes provide an explanation or justification of a particular section or preregistration item. Text contained in 'preregistration item' boxes requires a response."
authors:
  - Elliot Gould
  - Hannah Fraser
  - Libby Rumpff
  - Megan Good
  - Chris Jones
sidebar: false
bibliography: data/references.bib
toc-location: left
toc-expand: true
number-sections: true
---

@@

The following items pertain to properties of the *datasets* used for calibration (training), validation, and testing.

:::

::: callout-caution

## Preregistration Item

>>>>

---
title: "Adaptive Preregistration for Modelling"
subtitle: "A template suitable for use in Ecology and Conservation with accompanying rationale and explanation."
description: "Note: Black boxes provide an explanation or justification of a particular section or preregistration item. Text contained in 'preregistration item' boxes requires a response."
authors:
  - Elliot Gould
  - Hannah Fraser
  - Libby Rumpff
  - Jian Yen
  - Megan Good
  - Chris Jones
sidebar: false
bibliography: data/references.bib
toc-location: left
toc-expand: true
number-sections: true
---

@@

The following items pertain to properties of the *datasets* used for calibration (training), validation, and testing.
:::
